### 2019-03-13 _publications/jors/paper.tex
Sort out Makefile for latex build

\textcolor{blue}{keyword 1; keyword 2; etc. \\
Keywords should make it easy to identify who and what the software will be useful for.}

@@

\textcolor{blue}{An overview of the software, how it was produced, and the research for which it has been used, including references to relevant research articles. A short comparison with software which implements similar functionality should be included in this section. }

>>>>

phase-field; materials-science; jekyll-website; reproducible-science

@@

The phase-field method (PFM) describes material interfaces at the
mesoscopic scale between atomic scale models and macroscale models.
The PFM is well established and there are an assortment of code
frameworks (*e.g.*, Moose~\cite{moose}, PRISMS-PF~\cite{prisms-pf},
FiPy~\cite{fipy}, MMSP~\cite{mmsp}) available for solving the wide
variety of phenomena associated with phase-field (*e.g.*, dendritic
growth, spinodal decomposition, grain growth). However, phase-field
research groups often develop codes in isolation and do not publish
the code bases or do not support or distribute the code bases to the
wider community. PFHub is a community effort spearheaded by the Center
for Hierarchical Materials Design at Northwestern University and the
National Institute of Standards and Technology to support the
development of phase-field codes. The goal of PFHub is to improve
cross-collaboration between phase-field code developers and
practitioners by providing a standardized set of benchmark
problems~\cite{bm1, bm2} along with a web framework for uploading and
comparing benchmark results from different codes.
